---
title: "Let's get reproducible!"
author: "Helena Hartmann"
date: "23.09.2021"
output: github_document
---

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

The repository to this file can be found [here](https://github.com/helenahartmann/git_md_intro).


## Exercises

1. Edit the title of your header to change the title of your document. Add yourself as an author by adding 'author: "Your Name"' to the header in an extra line. Add today's date by adding 'date: "23.09.2021"' in an extra line. KNIT that document! What happens? -> md file is created, window opens

2. Change the output from “github_document” to “pdf_document”, knit and see what happens. Change it back to github_document afterwards. -> pdf opens

3. Rename the chunks you have to something that makes more sense than chunkname1, chunkname2 etc.

4. Have a look at the  chunk named data – why doesn’t it appear in the formatted file? How can we change that? -> change include to TRUE

5. Add some text to your document and change the formatting using *single asterisk* for italic or **double asterisk** for bold text.

6. Let's load some data about penguins! Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*. Now we are going to save that as a csv file.

7. Check out the knitted output for the plot chunk. Now add ', echo=FALSE' to the chunk producing the plot, knit it and see what changes.


## Including a chunk

```{r setup, include = TRUE}

# This is a code chunk. because we set the chunk options to include = FALSE, this chunk will not show up in our formatted output document of choice. Change this to TRUE to show the chunk.

knitr::opts_chunk$set(echo = TRUE)
# this option will set to show code and output for all chunks

2 + 3
```


## Including Text

You can include text just by writing in the file and using *RMarkdown* to edit the **formatting**. You can also include inline code: 

The mean speed of cars in the cars dataset is `r mean(cars$speed)` and the mean distance is `r mean(cars$dist)`. The dataset has `r nrow(cars)` observations.


## Including Code

You can include R code in the document as follows:

```{r table}
# change the chunkname above
summary(cars)
```

## Loading and displaying data

You can load some data about penguins.

```{r data, include = TRUE}

# load some data
install.packages("palmerpenguins")
library(palmerpenguins)
data = penguins

# Let's look at it
head(data)
table(data$species)

# Now we want to save it as a csv file
write.csv(data,'penguin_data.csv')
```

## Including Plots

You can also embed plots, for example:

```{r plot, echo = FALSE}
# change the chunkname above
# add ', echo=FALSE' to the chunk options above and see what changes in your output when you knit
plot(pressure)
```


## Sources

#### More information

Find some more information on RMarkdown and RNotebooks under [this link](https://argoshare.is.ed.ac.uk/healthyr_book/chap12-h1.html). 

#### Cheatsheets

Some cheatsheets can be found [here](https://raw.githubusercontent.com/rstudio/cheatsheets/master/rmarkdown-2.0.pdf) and [here](www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf).